\food{Orgasm Burgers}
\preptime{15 minutes}
\cooktime{15 minutes}
\people{4-6}

\recipe{
    \unit[1]{kg} & Ground Beef\\
    1 & Onion\\
    1 & Large, yolky egg\\
    2 & Brioche buns\\
    1 & Large on-the-vine tomato\\
    1 & Iceberg lettuce\\
    1 & Cucumber\\
    4 & Rashers of smoked back bacon\\
     & Butter\\
    \unit[80]{g} & Red Leicester cheese\\
     & BBQ sauce / ketchup\\
    \unit[3]{tbsp} & Pickled jalapeños\\
    \unit[1]{tbsp} & Olive oil\\
    Pinch & Salt\\
    Pinch & Pepper\\
}{
    \item Prep all the vegetative ingredients: slice the onion, tomato, cucumber, and lettuce.
    \item In a large bowl, mix the ground beef, egg, salt, and pepper.
    \item Form the beef into 4 patties.
    \item Heat the olive oil in a large pan on medium-high heat.
    \item Cook the patties for 3-4 minutes on each side.
    \item Add the cheese to the patties and cook for another 2 minutes.
    \item (Optional) Add the jalapeños to the pan and cook for another minute.
    \item Meanwhile, toast the brioche buns, and then butter them.
    \item Assemble the burgers: bun, lettuce, patty, bacon, tomato, cucumber, BBQ sauce, jalapenos, bun.
    \item Serve with fries, a cold beer, and moans of pleasure.
    \item After eating, take a nap. You've earned it.
}
%/photo{orgasm_burgers.jpg}

\info{This is a recipe that I've been perfecting for years. It's a real crowd-pleaser.
Dan called them "roofie burgers" because you eat them and then pass out.
Not because they contain roofies, to the best of my knowledge.
This is probably my favorite recipe, but Jenny and I worry about the health implications of eating this more than once a month.}

